\documentclass[11pt,a4paper]{article}

\usepackage[top=1.5cm,bottom=1.5cm,left=2cm,right=2cm]{geometry}
\usepackage[utf8]{inputenc}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\title{PySuggestion IntelliJ (PyCharm) plugin development journal}
\author{Yichen Lu}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This is the paper's abstract
\end{abstract}

\section{Basic Tutorials}
Action

Short cut for actions

Add Menu items, add-to-group

Replace text

Cursor place

\section{Inspect ML part of codeInspect ML part of code}

\subsection{Following instructions on GitHub and Run}

\subsection{Try to get model from the code}
Successfully run the code by following the instruction provided in their Git repo but one of the import file was missing. Email author.

Author replied. Turns out they renamed the import file but forgot to rename the import code. Their code is not well written.

\section{Code completion trigger and suggestion list}

\subsection{Completion contributor}

Hard to understand the structure of the code. Calls between classes.
Read IntelliJ source code. \texttt{/completion/CompletionContributor.java}

Using source code from idea-php-laravel-plugin as a reference to help me understand how to add item into the code suggestion list. Helpful class:
\texttt{/src/fr/adrienbrault/idea/symfony2plugin/codeInsight/completion/CompletionContributor.java}

Manage to change the funny text using \texttt{CompletionResultSet.addLookupAdvertisement(String)}

\texttt{PsiElement} provide the lookup parameter our suggestions are based on

We need to recognize current lookup parameter and provide different suggestions.

From source code comment of \texttt{CompletionContributor} class:

"In \texttt{CompletionContributor} you will be given a {com.intellij.codeInsight.completion.CompletionResultSet} which will match \texttt{LookupElement}s against its prefix matcher \texttt{CompletionResultSet.getPrefixMatcher()}. If the default prefix calculated by IntelliJ IDEA doesn't satisfy you, you can obtain another result set via \texttt{com.intellij.codeInsight.completion.CompletionResultSet.withPrefixMatcher(PrefixMatcher)} and feed your lookup elements to the latter.

It's one of the item's lookup strings (\texttt{LookupElement.getAllLookupStrings()} that is matched against prefix matcher."

To get prefix of caret, use \texttt{CompletionResultSet.getPrefixMatcher().getPrefix()}

Create LookupElement using LookupElementBuilder


\end{document}